---
title: "Bootstrap"
output: html_document
---

## Target

* What is Bootstrap
* Use boot pacakge

#### Key ideas

Treat the sample as if it were the population

#### What is good for

* Calculating standard error
* Forming confidence intervals
* Performaing hypothesis test
* Improving predictors

## Notes

* Can be useful for complicated statics
* Be careful near the boundaries
* Be careful with non0-linear function

## Import package
```{r}
library(ggplot2)
library(boot)
```

## Bootstrap Example
```{r}
set.seed(333)
x          <- rnorm(30)
n          <- 30000
bootMean   <- rep(NA, n)
sampleMean <- rep(NA, n)

for(i in 1:n) {bootMean[i]   <- mean(sample(x, replace = T))}
for(i in 1:n) {sampleMean[i] <- mean(rnorm(30))}

df <- data.frame(b = bootMean,
                 s = sampleMean)

ggplot(df) + 
    geom_density(aes(x = b)) +
    geom_density(aes(x = s), colour = "red")
```


## Example with boot package
```{r}
set.seed(333)
n <- 10000
sampleMean <- rep(NA, n)

for(i in 1:n) {sampleMean[i] <- mean(rnorm(30))}
meanFunc <- function(x, i) {mean(x[i])}
bootMean <- boot(x, meanFunc, n)

bootMean

df <- data.frame(b = bootMean$t,
                 s = sampleMean)

ggplot(df) + 
    geom_density(aes(x = b)) +
    geom_density(aes(x = s), colour = "red")
```

## Nuclear costs
```{r}
# normal
data("nuclear")

nuke.lm <- lm(log(cost) ~ date, data = nuclear)
plot(nuclear$date, log(nuclear$cost), pch = 20)
abline(nuke.lm, col = "red", lwd = 3)

# bootstrap
bs <- function(data, indices, formula) {
    d   <- data[indices,]
    fit <- lm(formula = formula, data = d)
    return(coef(fit))
}

result <- boot(data = nuclear, statistic = bs, R = 10000, 
               formula = log(cost) ~ date)
plot(density(result$t[,2]), col = "red", lwd = 3)
lines(rep(nuke.lm$coefficients[2], 10), seq(0, 8, length = 10),
      col = "blue", lwd = 3)

# Bootstrap confidence interval
boot.ci(result)
```

## Bootstrapping from a model (hypothesis test)
```{r}
nuke.lm <- lm(log(cost) ~ date, data = nuclear)
resid <- rstudent(nuke.lm)
fit0 <- fitted(lm(log(cost) ~ 1, data = nuclear))
newNuc <- cbind(nuclear, resid = resid, fit0 = fit0)

bs <- function(data, indices) {
    return(coef(glm(data$fit0 + data$resid[indices] ~ data$date, 
                    data = data)))
}

result <- boot(data = newNuc, statistic = bs, R = 1000)
plot(density(result$t[,2]), lwd = 2, col = "blue")
lines(rep(coef(nuke.lm)[2], 10), seq(0, 3, length = 10), 
      col = "red", lwd = 3)
```

## Bootstrapping non-linear statistics (median)
```{r}
set.seed(555)
n <- 1000
x <- rnorm(30)
sampleMed <- rep(NA, n)

for(i in 1:n) {
    sampleMed[i] <- median(rnorm(30))
}

medFunc <- function(x, i) {
    median(x[i])
}

bootMed <- boot(x, medFunc, n)
plot(density(bootMed$t), col = "red", lwd = 3)
lines(density(sampleMed), lwd = 3)
```

